Import and process AODV3 Level2 AOD20 from Aeronet

### 2019-07-30 Code/03_import_AOD_V3.Rmd
add notes

Plot AERONET AOD by time    
Plot the difference by time   
```{r}
plotly::ggplotly(
ggplot(data = aod_lst_terra, aes(x = stn_time, y = AOD_470nm, color = Site_Name)) + 
  geom_point(size = 0.5, alpha = 0.8) +
  theme_bw()
)

>>>>

Plot AERONET AOD by time    
Plot the difference by time

```{r}
plotly::ggplotly(
ggplot(data = aod_lst_terra, aes(x = stn_time, y = AOD_470nm, color = Site_Name)) + 
  geom_point(size = 0.5, alpha = 0.8) +
  theme_bw()
)
